---
title: "SOHO200"
format: 
  html:
      toc: true
execute: 
  echo: false
theme:
  light: flatly
  dark: darkly
---

# Who

You!

# What

The SOHO 200 is the ~~first~~ second edition of the South Hobart Metrogaine/Scavenger hunt! A metrogaine is a form or [rogaine](https://rogaine.asn.au/about/what-is-rogaining) held in an urban environment.

You get points by visiting the locations, which we call, "controls", which marked on the map.

To verify that you have visited a location, there are "found items" on most controls. E.g., "What is the serial number on the bin next to the post?"

There are also bonus points available on many controls. E.g., "If you spot a (live) platypus you get 500 bonus points"

The goal is to get the most number of points.

You can run the course in any order!

# Where / When

- 7th December, 2024.
- 11:30am briefing, 12pm start.
- Start: [Fruehauf](https://maps.app.goo.gl/7J42vca1r6bNys6GA) at 11am.
- End: 4pm [Preachers Bar](https://www.facebook.com/preachershobart)

```{r}
#| echo: false
library(leaflet)
leaflet() |> 
    addTiles() |> 
    addMarkers(lng = 147.3012348499976,
               lat = -42.893349257964054) |> 
     addPopups(lng = 147.3012348499976,
               lat = -42.893349257964054,
               popup = 'Here is the where the <b>SOHO 200 begins!</b>')
```

# Why?

It was created by Nick as a way to do something fun for his friends.

# How?

The maps were created using <https://oomap.dna-software.co.uk/>

This website was created using [Quarto](https://quarto.org/) + github + ✨magic.✨

# Previous events

* [SOHO100](http://soho100.njtierney.com/)

# Map

Map links will be provided 12(ish) hours before the event.

You will be able to download the map by clicking the links below

- [SoHo200 Map](soho-200-map.pdf)

# Clue sheet

Links to the clue sheets will be provided 24 hours before the event.

You will be able to download the clue sheet below:

- [clue sheet 1 pager](soho-200-clue-sheet-1p.pdf)
- [clue sheet 2 pager](soho-200-clue-sheet-2p.pdf)

You will also be able to see the clue sheet at this table below:

```{r}
#| eval: false
options(tidyverse.quiet = TRUE)
library(tidyverse)
library(googlesheets4)

soho200_url <- "https://docs.google.com/spreadsheets/d/1UIpkQ1_k-4to3QH7jOwangWykjwjHdBo_EuLbqjhO-s/edit?gid=0#gid=0"

soho200 <- read_sheet(soho200_url,
                      col_types = "ddccl")

write_csv(soho200, "soho200-data.csv")

```


```{r}
soho200 <- readr::read_csv("soho200-data.csv", show_col_types = FALSE)
DT::datatable(soho200,
              options = list(
                  pageLength = 38
              ))
```

You get 1 lifeline: Call Nick. However you get as many lifelines as you like if you call Nick from a Telstra phone booth (It's free, really!)

# Transport multipliers

- Horseback: 25x total points
- On Foot = 10x total points
- Cycling = 5x total points
- Car = 1x total points

These are calculated at the end of the game. 

Example: I walk half, and biked half. I get 10x0.5 plus 5x0.5. Giving a 7.5x total score multiplier.

# Cryptic Puzzle

Cryptic puzzle solve this and be there at the right time, get 400 bonus points. The Clues are either anagrams, numbers, or double definitions (two clues but the answer is a single word. 

1. Steal; cake machine; 
2. Waterslide Undy's (7,8); 
3. Spy; burrowing Creature; 
4. U burn log; 
5. kunanyi + Tasman Bridge Speed limit; 
6. (South Hobart Post Code divided by Number of Elizabeth Street Outdoor Stores) + Height of Fruehauf

Find: 1: _______ 
at 2: ________ ________, 
(Corner of 3 _______ & _______ ), 
between 5: _____ and 6: ______

# Set/Special Bonuses
* Make up your own set bonus, award your own (reasonable) points. Must justify at pub.
* Salamanca So Fresh Right now: Visit both Sal Fresh at SoHo and Salamanca. **100 points**
* Coffee flight: visit all café's: Bear With Me, Little Missy, Hamlet, Banjos **100 points**
* Ice cream run: Get an affogato at a cafe + Have an ice cream at van dieman's **200 points**
* Ice cream float: Complete ice cream run and also have a beer at New Sydney **300 points**
* Water world: Travel by water (boat, swim, etc!) between two controls, **get 10X pts for those controls. Add a note on those control scores**
* Starfish: Pull a starfish out of the water somewhere (put it back, too) in Hobart. **300 points.**
* Four Corners: Do controls 9, 30, 35, and 1 - **250 points**
* West Side: Controls 1-4, 20, 32-39 - bonus **100 points**
* Knock off knock lofty: do controls 37, 38, and 39. **100 points.**
* Academy Awards: Most controls visited - bonus **250 points**
* Echidna bonus: See an Echidna, bonus **500 points.**
* Monotreme bonus: See both a live platypus Echidna and Platypus - **2,000 points**
* Tag: Find and tag Nick betwen 2:30 and 3:30pm - **75 points**
* Birthday! Sing happy birthday to a friend/stranger. Must be their birthday. Can be over the phone/video. **90 points.**
* Swifty bonus: See a (live) swift parrot - **1,000 points**
* Fully Swifty: Monotreme bonus + Swifty bonus: **10X your total score.**
* Singing in the rain. Sing a song at Salamanca Markets in this amazing weather window we have. **99 points.**
* Rain related costume. If you wear comedic water gear (snorkel, wetsuit, rubber ducky) for the soho you get an additional **99 points.**

# Hobart Celebrities to get photos with (100 points per celebrity)

* David Walsh 
* Bob Brown
* Hannah Moloney
* Santa Claus
* Someone you think is a celebrity?

# Rainy Day Activities
* Play a game of chess at one of the Café's - **25 points**
* Play a game of chess with a stranger - **100 points**
* Play a board game at a café - **50 points**
* Visit MONA - **50 points**
* Watch Lord of the Rings, Fellowship of the Ring - **178 points**
* Start and finish a book - **points per page**
* **Decide to brave the rain and do the SoHo200: Bonus 500 points.**
