---
title: "SOHO200"
format: 
  html:
      toc: true
execute: 
  echo: false
theme:
  light: flatly
  dark: darkly
---

# Who

You!

# What

The SOHO 200 is the ~~first~~ second edition of the South Hobart Metrogaine/Scavenger hunt! A metrogaine is a form or [rogaine](https://rogaine.asn.au/about/what-is-rogaining) held in an urban environment.

You get points by visiting the locations, which we call, "controls", which marked on the map.

To verify that you have visited a location, there are "found items" on most controls. E.g., "What is the serial number on the bin next to the post?"

There are also bonus points available on many controls. E.g., "If you spot a (live) platypus you get 500 bonus points"

You can run the course in any order!

Travel by foot to get a 10X bonus
Travel by bike to get a 5X bonus
Travel by car to get a 1X bonus
Travel by horse to get a 25X bonus

You can also use a proportion of each, if you like. So, ride somewhere, then run, or drive, ride, run, etc.

The goal is to get the most number of points.

You can run the course in any order!

# Where / When

- 7th December, 2024.
- 10:30am briefing, 11am start.
- Start: [Fruehauf](https://maps.app.goo.gl/7J42vca1r6bNys6GA) at 11am.
- End: 3pm TBA

```{r}
#| echo: false
library(leaflet)
leaflet() |> 
    addTiles() |> 
    addMarkers(lng = 147.3012348499976,
               lat = -42.893349257964054) |> 
     addPopups(lng = 147.3012348499976,
               lat = -42.893349257964054,
               popup = 'Here is the where the <b>SOHO 200 begins!</b>')
```

# Why?

It was created by Nick as a way to do something fun for his friends.

# How?

The maps were created using <https://oomap.dna-software.co.uk/>

This website was created using [Quarto](https://quarto.org/) + github + ✨magic.✨

# Previous events

* [SOHO100](http://soho100.njtierney.com/)

# Map

Map links will be provided 24 hours before the event.

You will be able to download the map by clicking the links below

- [A MAP WILL BE HERE]

# Clue sheet

Links to the clue sheets will be provided 24 hours before the event.

You will be able to download the clue sheet below:

- [clue sheet 2 pager]
- [clue sheet 1 pagr]

You will also be able to see the clue sheet at this table below:

```{r}
#| eval: false
options(tidyverse.quiet = TRUE)
library(tidyverse)

soho100 <- read_csv("soho-100-data.csv",
                    show_col_types = FALSE,
                    n_max = 32)

DT::datatable(soho100,
              options = list(
                  pageLength = 33
              ))
```

# Extra point challenges


# Bonus point multipliers

* Visit all cafes on the list = 30 points. 
* Echidna bonus: 500 points. if you see a (live) Echidna
* Monotreme bonus:  1000 points for seeing both a live platypus and live echidna.


# Transport multiplies

* Horseback = 25x total points
* On Foot = 10x total points
* Cycling = 5x total points
* Car = 1x total points
* % of each also allowed
